```{r}
library(entropart)
library(boot)
library(vegan)
library(simboot)
library(openxlsx)
#install.packages("simboot")
```


```{r}
data_1=read.csv("Hebdo I neg.csv",T,sep=',')
nrow(data_1)
data_2=read.csv("hebdo I pos.csv",T,sep=',')
nrow(data_2)
data_3=read.csv("hebdo we neg.csv",T,sep=',')
nrow(data_3)
data_4=read.csv("Hebdo we pos.csv",T,sep=',')
nrow(data_4)
```




Obtained Results using chaowong Jost Adjustment I - 6.2 WE - 7.05

Existing results I- 6.17 WE - 7.01

Obtaining Frequencies for pronouns “I” and “WE” with polarities “POS” and “NEG”

```{r}
fWith_I_POS = data_2$freq
fWith_I_NEG = data_1$freq
fWith_WE_POS = data_4$freq
fWith_WE_NEG = data_3$freq
```



Entropy for pronouns “I” and “WE” with polarities “POS” and “NEG”


```{r}
HWith_I_POS = Shannon(fWith_I_POS)/log(2)
HWith_I_NEG = Shannon(fWith_I_NEG)/log(2)
HWith_WE_POS = Shannon(fWith_WE_POS)/log(2)
HWith_WE_NEG = Shannon(fWith_WE_NEG)/log(2)

HWith_I_POS
HWith_I_NEG
HWith_WE_POS
HWith_WE_NEG
```


Obtained Results:

I POS - 5.37 I NEG - 5.01 WE POS - 6.11 WE NEG - 6.19

Existing Results:

I POS - 5.34 I NEG - 4.99 WE POS - 6.08 WE NEG - 6.13

CI For I

```{r}
#estShannon(fWith_I)
Actual_entropy =Shannon(fWith_I)/log(2)
LB=(Shannon(fWith_I)-estShannon(fWith_I)$varest)/log(2)
UB=(Shannon(fWith_I)+estShannon(fWith_I)$varest)/log(2)
Actual_entropy
LB
UB
```
 CI 
 
 LB - 6.201603
 UB - 6.201956
 
 calculated shannon entropy - 6.20178

CI for WE
```{r}
Actual_entropy =Shannon(fWith_WE)/log(2)
LB=(Shannon(fWith_WE)-estShannon(fWith_WE)$varest)/log(2)
UB=(Shannon(fWith_WE)+estShannon(fWith_WE)$varest)/log(2)
Actual_entropy
LB
UB
```

 CI 
 
 LB - 7.052101
 UB - 7.052536 
 calculated shannon entropy - 7.052318
 
 CI for I-POS
```{r}
ntweets_I_POS  = length(fWith_I_POS)
Actual_entropy =Shannon(fWith_I_POS)/log(2)
LB=(Shannon(fWith_I_POS)-estShannon(fWith_I_POS)$varest)/log(2)
UB=(Shannon(fWith_I_POS)+estShannon(fWith_I_POS)$varest)/log(2)
Actual_entropy
LB
UB
```
 CI for I-POS 
 
 LB - 5.3737
 UB - 5.374283 
 calculated shannon entropy - 5.373991
 
 CI For I-NEG
```{r}
ntweets_I_NEG  = length(fWith_I_NEG)
Actual_entropy =Shannon(fWith_I_NEG)/log(2)
LB=(Shannon(fWith_I_NEG)-estShannon(fWith_I_NEG)$varest)/log(2)
UB=(Shannon(fWith_I_NEG)+estShannon(fWith_I_NEG)$varest)/log(2)
Actual_entropy
LB
UB
```
CI for I-NEG 
 
 LB - 5.01863
 UB - 5.01952
 calculated shannon entropy - 5.019075
 
CI for WE-POS 
```{r}
ntweets_WE_POS  = length(fWith_WE_POS)
Actual_entropy =Shannon(fWith_WE_POS)/log(2)
LB=(Shannon(fWith_WE_POS)-estShannon(fWith_WE_POS)$varest)/log(2)
UB=(Shannon(fWith_WE_POS)+estShannon(fWith_WE_POS)$varest)/log(2)
Actual_entropy
LB
UB
```
 CI for WE-POS
 
 LB - 6.113955
 UB - 6.114597
 calculated shannon entropy - 6.114276


CI for WE-NEG
```{r}
ntweets_WE_NEG  = length(fWith_WE_NEG)
Actual_entropy =Shannon(fWith_WE_NEG)/log(2)
LB=(Shannon(fWith_WE_NEG)-estShannon(fWith_WE_NEG)$varest)/log(2)
UB=(Shannon(fWith_WE_NEG)+estShannon(fWith_WE_NEG)$varest)/log(2)
Actual_entropy
LB
UB

#(Shannon(fWith_WE_NEG)+sqrt(estShannon(fWith_WE_NEG)$varest)*2)/log(2)
``` 


 CI for WE-NEG 
 
 LB - 6.192856
 UB - 6.19398
 calculated shannon entropy - 6.193418
 
 